Paper Visualization

### 2024-09-01 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
changing things

```{r Top Terms}
# Display the top terms for each topic
top_terms <- terms(lda_model, 20)
print(top_terms)

# Visualize the top terms for each topic (concise visualization)
top_terms_df <- tidy(lda_model, matrix = "beta") %>%
  group_by(topic) %>%
  top_n(20, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

# Plotting the top terms for each topic
ggplot(top_terms_df, aes(reorder_within(term, beta, topic), beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free_y") +
  coord_flip() +
  scale_x_reordered() +
  labs(title = "Top Terms in Each Topic", x = "Term", y = "Beta") +
  theme_minimal()
```

>>>>

```{r Top Terms}
# Load required libraries
library(tidyr)
library(dplyr)
library(sjPlot)

# Assuming top_terms_df is your data frame from the LDA analysis

# Reshape the data frame to have each topic's terms and betas side by side
reshaped_df <- top_terms_df %>%
  group_by(topic) %>%
  mutate(term_id = row_number()) %>%
  ungroup() %>%
  pivot_wider(
    names_from = topic,
    values_from = c(term, beta),
    names_glue = "Topic_{topic}_{.value}"
  )

reshaped_df <- reshaped_df %>%
  select(term_id, 
         starts_with("Topic_1_term"), starts_with("Topic_1_beta"),
         starts_with("Topic_2_term"), starts_with("Topic_2_beta"),
         starts_with("Topic_3_term"), starts_with("Topic_3_beta"),
         starts_with("Topic_4_term"), starts_with("Topic_4_beta"),
         starts_with("Topic_5_term"), starts_with("Topic_5_beta"))

# Create a styled table using sjPlot
# tab_df(
#  reshaped_df,
#  title = "Top Terms and Betas for Each Topic",
#  show.rownames = FALSE,
#  digits = 2,
#  file = output_file_path
#  )

library(dplyr)
library(gt)

# Create the gt table
gt_table <- reshaped_df %>%
  gt() %>%
  tab_spanner(
    label = "Topic 1",
    columns = c("Topic_1_term", "Topic_1_beta")
  ) %>%
  tab_spanner(
    label = "Topic 2",
    columns = c("Topic_2_term", "Topic_2_beta")
  ) %>%
  tab_spanner(
    label = "Topic 3",
    columns = c("Topic_3_term", "Topic_3_beta")
  ) %>%
  tab_spanner(
    label = "Topic 4",
    columns = c("Topic_4_term", "Topic_4_beta")
  ) %>%
  tab_spanner(
    label = "Topic 5",
    columns = c("Topic_5_term", "Topic_5_beta")
  ) %>%
  cols_label(
    term_id = "Term No.",
    Topic_1_term = "term", Topic_1_beta = "beta",
    Topic_2_term = "term", Topic_2_beta = "beta",
    Topic_3_term = "term", Topic_3_beta = "beta",
    Topic_4_term = "term", Topic_4_beta = "beta",
    Topic_5_term = "term", Topic_5_beta = "beta"
  )

gt_table

# Save the gt table to an HTML file
output_file_path <- file.path(output_directory, "images and tables", "Top Terms and Betas for Each Topic.html")
gtsave(gt_table, output_file_path)
```
